---
title: "LOL_Dataset_Project"
author: "Tamana Yaqoubi, Veronica Alviso"
date: "2025-11-04"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(gridExtra)
library(plotly)
library(shiny)
library(here)
source("R_Data_Prep.R")
#data_dir <- here::here(".")

```

## Read csv files
```{r}
'
championTbl <- read_tbl("ChampionTbl")
itemTbl<- read_tbl("ItemTbl")
matchStatsTbl <- read_tbl("MatchStatsTbl")
matchTbl <- read_tbl("MatchTbl")
RankTbl <- read_tbl("RankTbl")
SummonerMatchTbl <- read_tbl("SummonerMatchTbl")
TeamMatchTbl <- read_tbl("TeamMatchTbl")
'
```

## View datasets
```{r}
head(championTbl) %>% knitr::kable()
head(itemTbl) %>% knitr::kable()
head(matchStatsTbl) %>% knitr::kable()
head(matchTbl) %>% knitr::kable()
head(RankTbl, n = 11) %>% knitr::kable()
head(SummonerMatchTbl) %>% knitr::kable()
head(TeamMatchTbl) %>% knitr::kable()

```


## Champion Table -VA

The following the data set has basically an NA value named 'No champion'. The data set has been updated so that it only represents actual champions that are playable in League of Legends.

```{r}
championTbl <- championTbl %>% 
  filter(ChampionId > 0)
head(championTbl)
```

As you can see, there is no longer a champion ID 0 - No champion. Using the dplyr function filter we successfully removed any irrelevant or not needed rows. 

## MSI Table -TY
Creating a new table called 'MSI_Tbl' to join the Match Stats table and Item Table


```{r}
'
MSI_Tbl <- full_join(matchStatsTbl, itemTbl, 
                     by = join_by(item1 == ItemID),
                     suffix = c("", "_1"))

MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item2 == ItemID), 
                     suffix = c("", "_2"))

MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item3 == ItemID), 
                     suffix = c("", "_3"))

MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item4 == ItemID), 
                     suffix = c("", "_4"))


MSI_Tbl  <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item5 == ItemID), 
                     suffix = c("", "_5"))


MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item6 == ItemID), 
                     suffix = c("", "_6"))

MSI_Tbl
'
```



## match_rank Table -VA

We have created a new table called match_rank_tbl.
The purpose of this table is to join both the match table and the rank table by their RankFk == RankId. This will let us know whether the match was ranked or unranked.

```{r}
'match_rank_tbl <- full_join(matchTbl,RankTbl,join_by(RankFk == RankId))'
head(match_rank_tbl)
```



## TMR Tbl -TY
Create new table called 'TMM_Tbl' to join Team Match Table and Match Table


```{r}
'TMR_Tble <- full_join(TeamMatchTbl, match_rank_tbl, by = join_by(MatchFk == MatchId))'
TMR_Tble
```



## SMR tbl -VA

The following table was created in order to join both the summoner match table and a match rank table.
This table displays a smaller depiction 


```{r}
'SMR_Tbl <- full_join(SummonerMatchTbl, championTbl, join_by(ChampionFk == ChampionId))

SMR_Tbl <- full_join(SMR_Tbl, match_rank_tbl, by = join_by(MatchFk == MatchId))'
head(SMR_Tbl)
```

## Joining SMR table and MSI table -TY
```{r}
#SMRI_tbl <- full_join(SMR_Tbl, MSI_Tbl, by = join_by(SummonerMatchId==SummonerMatchFk))
#SMRI_tbl 
#Needs further filtering 
```



## Tamana MSI_tbl and Match_rank_tbl dplyr and plot functions

1. MSI_tbl How many SummonerMatchFk play more than one lane


```{r}

```


2. MSI_tbl Mean, Median, Max, Min minions killed, TurretDmg, DmgTaken, DmgDealt, totalGold.


```{r}

```


3. MSI_tbl create new column (boolean) for indicating win or lose. Filter to win and lose only and create a ggplots.

```{r}

```


4. MSI_tbl (ask professor) Items, filter remove NAs, count total items, most popular items, least popular items. Median qne mean items a player holds. 


```{r}

```


5. Line plot game duration as the Y value and Queue type as the X value, filter based on RankName.


```{r}

```


6. Plot game duration density 


```{r}

```































































## Veronica

1. TMR_tbl create column (boolean) indicating who won.

```{r}
head(TMR_Tble)
```


2. TMR_tbl Filter teams with winning arams, classics based on rank. Bar graph & scatter plot x = rank, y = # of wins, color by queue types, density. face wrap

Let us look at all winning teams from each map type.
```{r}
source(here::here("WinningTeams","app.R"))
shinyApp(ui, server) 
head(Team_Winner_Tbl, n = 10) 
```


3. TMR_tbl Filter winning teams, most used champion in red team and blue team 

```{r}



```


4. TMR_tbl find the mean, median, max and min (all kills) only for classic queue types

```{r}

TMR_Tble %>%
  filter(QueueType == "CLASSIC") %>% 
  summarise(
    Total_Mean_Kills = mean(RedKills + BlueKills, na.rm = TRUE),
    Total_Medium_Kills = median(RedKills + BlueKills, na.rm = TRUE),
    Max_Kills = max(RedKills + BlueKills, na.rm = TRUE),
    Red_Mean = mean(RedKills, na.rm = TRUE),
    Blue_Mean = mean(BlueKills, na.rm = TRUE),
    Red_Median = median(RedKills, na.rm = TRUE),
    Blue_Median = median(BlueKills, na.rm = TRUE),
    Red_Max = max(RedKills, na.rm = TRUE),
    Blue_Min = max(BlueKills, na.rm = TRUE)
    )
  
```


```{r}

```

5. TMR_tbl Count the number game plays per queue types plot

```{r}
ggplotly( ggplot(TMR_Tble,aes(x = QueueType, fill = QueueType, text = paste("Count:", after_stat(count)))) + geom_bar(), tooltip = "text")
```


7. SMR_tbl: Top 10 people that play: Queue types. - instead found each player and the amount of games they play per queue type 

```{r}
Player_Games <- SMR_Tbl %>% 
  select(SummonerFk,QueueType,RankFk,RankName) %>% 
  group_by(QueueType, SummonerFk, RankName) %>%
  summarise(games = n()) %>% 
  arrange(SummonerFk)
  
Temp
ggplotly(ggplot(Player_Games,aes(x = QueueType, fill = QueueType, text = paste("Count:", after_stat(count)))) + geom_bar(), tooltip = "text", na.rm = TRUE)

#ggplotly(ggplot(Player_Games,aes(x = QueueType, y = RankName, color = QueueType) + geom_bar(), tooltip = "text", na.rm = TRUE)

```

```


8. SMR_tbl:  Histogram champions

```{r}
#CHANGE

```


9. SMR_tbl: Filter MSI_table to only have matchID and wins. Join with SMR table. Calculate the top 10 players with the most wins.

```{r}

```

