---
title: "LOL_Dataset_Project"
author: "Tamana Yaqoubi, Veronica Alviso"
date: "2025-11-04"
output: html_document
runtime: shiny
---

## About the dataset 
https://www.kaggle.com/datasets/nathansmallcalder/lol-match-history-and-summoner-data-80k-matches

- The data comes from League of legends (European Region). 
- Shows team analysis and per player analysis providing insight stats in KDA, items, characters "champions', winning, etc 
- The dataset comes from Kaggle.com
##Introduction 
This dataset provides comprehensive match and player information from League of Legends, one of the world’s most popular multiplayer online battle arena (MOBA) games. It features data from 35,000 matches and over 78,000 player records, covering various in-game aspects such as champion choices, performance metrics, match results, and other gameplay statistics. This dataset consist of 7 tables: MatchStatsTbl, TeamMatchStatsTbl, MatchTbl, RankTble, ChampionTbl, ItemTbl, SummonerTbl, and SummonerMatchTbl. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(gridExtra)
library(plotly)
library(shiny)
library(here)
source("R_Data_Prep.R")
#data_dir <- here::here(".")

```

## Read csv files
```{r, echo = FALSE}
'
championTbl <- read_tbl("ChampionTbl")
itemTbl<- read_tbl("ItemTbl")
matchStatsTbl <- read_tbl("MatchStatsTbl")
matchTbl <- read_tbl("MatchTbl")
RankTbl <- read_tbl("RankTbl")
SummonerMatchTbl <- read_tbl("SummonerMatchTbl")
TeamMatchTbl <- read_tbl("TeamMatchTbl")
'
```
---

## View Original datasets
```{r}
head(championTbl) %>% knitr::kable()
head(itemTbl) %>% knitr::kable()
head(matchStatsTbl) %>% knitr::kable()
head(matchTbl) %>% knitr::kable()
head(RankTbl, n = 11) %>% knitr::kable()
head(SummonerMatchTbl) %>% knitr::kable()
head(TeamMatchTbl) %>% knitr::kable()

```

---

## Modified Tables

What we did is join most of our data sets to have a more efficient data structure. The following data sets were created:
 - match_rank_tbl : This table displays every match in EU region with the following information: Queue type, Rank, Game duration. 
 - MSI_Tbl : This data set will display the players detailed match stats which include kills for both enemy champions and monsters affiliated and include item purchase and summoner spells.
 - SMR_Tbl : This data set displays the players detailed 


```{r, echo =FALSE}
head(match_rank_tbl)
head(TMR_Tble)
head(SMR_Tbl)
```

---

## Joining SMR table and MSI table -TY
```{r}
#SMRI_tbl <- full_join(SMR_Tbl, MSI_Tbl, by = join_by(SummonerMatchId==SummonerMatchFk))
#SMRI_tbl 
#Needs further filtering 
```

---

## Tamana MSI_tbl and Match_rank_tbl dplyr and plot functions

#MSI_Tbl

1. How many SummonerMatchFk play more than one lane


```{r, echo=FALSE}
MSI_Tbl %>%
  group_by(SummonerMatchFk)%>%
  summarise(num_lanes = n_distinct(Lane))%>% #count the unique lanes
  filter(num_lanes > 1)%>%
  summarise(total_players = n())

```


2. Find the Mean, Median, Max, and Min for the following:
- minions killed
- TurretDmg
- DmgTaken
- DmgDealt
- totalGold.


Mean median min and max of minions killed: 
```{r, echo = F}
# mean, median, min, and max of Minions Killed
MSI_Tbl%>%
  summarise(avg_minionsKilled = mean(MinionsKilled, na.rm = T),
            median_minionsKilled = median(MinionsKilled, na.rm = T),
            min_minionsKilled = min(MinionsKilled, na.rm = T),
            max_minionsKilled = max(MinionsKilled, na.rm = T))
```

Mean median min and max of Turret Damage killed:
```{r, echo=FALSE}

# mean, median, min, and max of TurretDmg
MSI_Tbl%>%
  summarise(avg_TurretDmgDealt = mean(TurretDmgDealt, na.rm = T),
            median_TurretDmgDealt = median(TurretDmgDealt, na.rm = T),
            min_TurretDmgDealt = min(TurretDmgDealt, na.rm = T), 
            max_TurretDmgDealt = max(TurretDmgDealt, na.rm = T))
```

Mean median min and max of Damage Taken killed:
```{r, echo=FALSE}
# mean, median, min, and max of DmgTaken
MSI_Tbl%>%
  summarise(avg_DmgTaken = mean(DmgTaken, na.rm = T),
            median_DmgTaken = median(DmgTaken, na.rm = T), 
            min_DmgTaken = min(DmgTaken, na.rm = T),
            max_DmgTaken = max(DmgTaken, na.rm = T))
```

Mean median min and max of Damage Dealt killed:
```{r, echo=FALSE}
# mean, median, min, and max of DmgDealt
MSI_Tbl%>%
  summarise(avg_DmgDealt = mean(DmgDealt, na.rm = T),
            median_DmgDealt = median(DmgDealt, na.rm = T), 
            min_DmgDealt = min(DmgDealt, na.rm = T),
            max_DmgDealt = max(DmgDealt, na.rm = T))
```

Mean median min and max of total gold killed:
```{r,echo=FALSE}
# mean, median, min, and max of totalGold
MSI_Tbl%>%
  summarise(avg_TotalGold = mean(TotalGold, na.rm = T),
            median_TotalGold = median(TotalGold, na.rm = T), 
            min_TotalGold = min(TotalGold, na.rm = T),
            max_TotalGold = max(TotalGold, na.rm = T))
```

---

3. Create new column (boolean) for indicating win or lose. Filter to win and lose only and create a ggplots.

```{r, echo=FALSE}
MSI_Tbl%>%
  mutate(won = Win != 0)%>%
  drop_na(won)%>% 
  ggplot(aes(x=won, fill=won)) + 
  geom_bar() +
  labs(title = "Win vs. Lose",
       x = "results",
       y = "count")
```


4. MSI_tbl (ask professor) Items, filter remove NAs, count total items, most popular items, least popular items. Median qne mean items a player holds. 


```{r}
#Lost and confused about this part, will have to ask the professor 
MSI_Tbl%>%
  drop_na(item1, item2, item3, item4, item5, item6)
```
---

5. Line plot game duration as the Y value and Queue type as the X value, filter based on RankName.


```{r}
match_rank_tbl %>%
  group_by(RankName)%>%
  summarise(Duration= n())

ggplot(match_rank_tbl, aes(color= QueueType,x = GameDuration)) + 
  geom_density() + 
  labs(title = "Game Duration",
  x = "Queue Type",
  y = "Time")
```


6. Plot game duration density 


```{r}
ggplot(match_rank_tbl, aes(x=GameDuration, fill = QueueType)) +
  geom_density() +
  labs(title = "Game Duration") + 
  facet_wrap(~QueueType)
```
---

# Created a new column called SecondLane 
```{r, echo=FALSE}
MSI_Tbl %>% 
   group_by(SummonerMatchFk) %>% 
  filter(n()>1) %>%   
  distinct(SummonerMatchFk, Lane, .keep_all = TRUE) %>% 
  arrange(SummonerMatchFk) %>%   
  filter(n()>1) %>% 
  group_by(SummonerMatchFk) %>% 
  mutate(tally_person = row_number()) %>% 
  filter(tally_person == 2) -> table2

MSI_Tbl %>% 
   group_by(SummonerMatchFk) %>% 
  filter(n()>1) %>%   
  distinct(SummonerMatchFk, Lane, .keep_all = TRUE) %>% 
  arrange(SummonerMatchFk) %>%   
  filter(n()>1) %>% 
  group_by(SummonerMatchFk) %>% 
  mutate(tally_person = row_number()) %>% 
  filter(tally_person == 1) %>%  
  select(SummonerMatchFk, SecondLane = Lane) -> table1

MSI_Tbl_doubles <- full_join(table1, table2, join_by(SummonerMatchFk))
rm(table1)
rm(table2)


MSI_Tbl <- MSI_Tbl %>% 
  group_by(SummonerMatchFk) %>% 
  anti_join(MSI_Tbl_doubles, join_by(SummonerMatchFk)) %>%
  mutate(SecondLane = NA) %>% 
  rbind(MSI_Tbl_doubles) %>% 
  distinct(SummonerMatchFk, .keep_all = TRUE) %>%
  select(-tally_person, -item1,-item2,-item3,-item4,-item5,-item6) %>% 
  arrange(SummonerMatchFk) 

rm(MSI_Tbl_doubles)

```

#Second Lane Data analysis for MSI Kills Column
```{r}
 MSI_Tbl %>% 
  select(SecondLane,kills) %>% 
  drop_na(SecondLane) %>% 
  group_by(SecondLane) %>%
  count(SecondLane, wt = kills) %>% 
  rename(kills = n) %>% 
  view()

```


#Second Lane Data analysis for MSI Kills Column plot
```{r, echo=FALSE}
ggplotly(ggplot( MSI_Tbl %>% 
  select(SecondLane,kills) %>% 
  drop_na(SecondLane) %>% 
  group_by(SecondLane) %>%
  count(SecondLane, wt = kills) %>% 
  rename(kills = n), 
  aes(x = SecondLane, y = kills, fill = SecondLane, text = paste("Count:", after_stat(y))))
  + geom_col(), 
  tooltip = "text", 
  na.rm = TRUE )

```


#Lane Data analysis for MSI kills Column 
```{r}
 MSI_Tbl %>% 
  drop_na(Lane) %>% 
  group_by(Lane) %>%
  count(Lane, wt = kills) %>% 
  rename(kills = n) %>% 
  view()
```

#Lane Data analysis for MSI Kills Column plot
```{r}
ggplotly(ggplot( MSI_Tbl %>% 
  select(Lane,kills) %>% 
  drop_na(Lane) %>% 
  group_by(Lane) %>%
  count(Lane, wt = kills) %>% 
  rename(kills = n), 
  aes(x = Lane, y = kills, fill = Lane, text = paste("Count:", after_stat(y))))
  + geom_col(), 
  tooltip = "text", 
  na.rm = TRUE )

```



#Combine SMR and MSI Table 
```{r}

```





























```{r}

```






## Veronica

1. TMR_tbl create column (boolean) indicating who won. Lets combine TMR with Champion Table 

```{r}


```


2. TMR_tbl Filter teams with winning arams, classics based on rank. Bar graph & scatter plot x = rank, y = # of wins, color by queue types, density. face wrap

Let us look at all winning teams from each map type.
```{r}
#source(here::here("WinningTeams","app.R"))
#shinyApp(ui, server) 
#head(Team_Winner_Tbl, n = 10) 
```


3. TMR_tbl Filter winning teams, most used champion in red team and blue team 

```{r}



```


4. TMR_tbl find the mean, median, max and min (all kills) only for classic queue types

```{r}

TMR_Tble %>%
  filter(QueueType == "CLASSIC") %>% 
  summarise(
    Total_Mean_Kills = mean(RedKills + BlueKills, na.rm = TRUE),
    Total_Medium_Kills = median(RedKills + BlueKills, na.rm = TRUE),
    Max_Kills = max(RedKills + BlueKills, na.rm = TRUE),
    Red_Mean = mean(RedKills, na.rm = TRUE),
    Blue_Mean = mean(BlueKills, na.rm = TRUE),
    Red_Median = median(RedKills, na.rm = TRUE),
    Blue_Median = median(BlueKills, na.rm = TRUE),
    Red_Max = max(RedKills, na.rm = TRUE),
    Blue_Min = max(BlueKills, na.rm = TRUE)
    )

```


Team winner table mean min max of the for Both teams : Kills, Baron, Rift Herald, Dragon, Towers

```{r}
  
Team_Winner_Stats <-Team_Winner_Tbl %>%
  filter(Side %in% c("Red","Blue")) %>%
  filter(QueueType %in% c("CLASSIC", "ARAM","SWIFTPLAY","ULTBOOK")) %>% 
  group_by(Side, QueueType) %>% 
  summarise(MeanKills = mean(Kills, na.rm = TRUE),
            MinKills = min(Kills, na.rm = TRUE),
            MaxKills = max(Kills, na.rm = TRUE),
            MeanBaron = mean(BaronKills, na.rm = TRUE),
            MinBaron = min(BaronKills, na.rm = TRUE),
            MaxBaron = max(BaronKills, na.rm = TRUE),
            MeanRiftHeraldKills = mean(RiftHeraldKills, na.rm = TRUE),
            MinRiftHeraldKills = min(RiftHeraldKills, na.rm = TRUE),
            MaxRiftHeraldKills = max(RiftHeraldKills, na.rm = TRUE),
            MeanDragonKills = mean(DragonKills, na.rm = TRUE),
            MinDragonKills = min(DragonKills, na.rm = TRUE),
            MaxDragonKills = max(DragonKills, na.rm = TRUE),
            MeanTowerKills = mean(TowerKills, na.rm = TRUE),
            MinTowerKills = min(TowerKills, na.rm = TRUE),
            MaxTowerKills = max(TowerKills, na.rm = TRUE))

view(Team_Winner_Stats)
```


```{r}

```

```{r}

  
```

# Bar plot 
```{r}
ggplotly(ggplot(Team_Winner_Stats, aes(x = QueueType, y = MeanKills, fill = Side,text = paste("Count:", after_stat(y)))) + geom_col() + facet_wrap(~Side), tooltip = "text")
```

```{r}
ggplotly(ggplot(Team_Winner_Stats %>% 
                  filter(QueueType!= "ARAM"), aes(x = QueueType, y = MeanBaron, fill = Side,text = paste("Count:", after_stat(y)))) + geom_col() + facet_wrap(~Side), tooltip = "text")
```

```{r}
ggplotly(ggplot(Team_Winner_Stats %>% 
                  filter(QueueType!= "ARAM"), aes(x = QueueType, y = MeanRiftHeraldKills, fill = Side,text = paste("Count:", after_stat(y)))) + geom_col() + facet_wrap(~Side), tooltip = "text")
```


7.each player and the amount of games they play per queue type 

```{r}
Player_Games <- SMR_Tbl %>% 
  select(SummonerFk,QueueType,RankFk,RankName) %>% 
  group_by(QueueType, SummonerFk, RankName) %>%
  summarise(games = n()) %>% 
  arrange(SummonerFk)

```

How many players play in each queue type, a player can play multiple queue types in league of legends. No map restriction.
```{r}

ggplotly(ggplot(Player_Games,aes(x = QueueType, fill = QueueType, text = paste("Count:", after_stat(count)))) + geom_bar(), tooltip = "text", na.rm = TRUE)

```

```{r}
Player_Games %>%
  group_by(RankName) %>% 
  distinct(SummonerFk,.keep_all = TRUE) %>% 
  summarise(n=n()) %>% 
  drop_na(RankName) %>% 
  rename(Players = n)
```


What rank players fall in in this data set. 

```{r}
ggplotly(ggplot(Player_Games %>%
  group_by(RankName) %>% 
  distinct(SummonerFk,.keep_all = TRUE) %>% 
  summarise(n=n()) %>% 
  drop_na(RankName) %>% 
  rename(Players = n),aes(x = RankName, y = Players, fill = RankName, text = paste("Count:", after_stat(y)))) + geom_col(), tooltip = "text", na.rm = TRUE)

```

Fun fact: 
```{r}

```

