---
title: "LOL_Dataset_Project"
author: "Tamana Yaqoubi, Veronica Alviso"
date: "2025-11-04"
output: 
  html_document:
    self_contained: false      
    highlight: null
    pandoc_args: ["--syntax-highlighting=none"]
#runtime: shiny
---

## About the dataset 
https://www.kaggle.com/datasets/nathansmallcalder/lol-match-history-and-summoner-data-80k-matches

- The data comes from League of legends (European Region). 
- Shows team analysis and per player analysis providing insight stats in KDA, items, characters "champions', winning, etc 
- The dataset comes from Kaggle.com
##Introduction 
This dataset provides comprehensive match and player information from League of Legends, one of the world’s most popular multiplayer online battle arena (MOBA) games. It features data from 35,000 matches and over 78,000 player records, covering various in-game aspects such as champion choices, performance metrics, match results, and other gameplay statistics. This dataset consist of 7 tables: MatchStatsTbl, TeamMatchStatsTbl, MatchTbl, RankTble, ChampionTbl, ItemTbl, SummonerTbl, and SummonerMatchTbl. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(gridExtra)
library(plotly)
library(shiny)
library(here)
library(knitr)
source("R_Data_Prep.R")
#data_dir <- here::here(".")

```

## Read csv files
```{r, echo = FALSE}

# championTbl <- read_tbl("ChampionTbl")
# itemTbl<- read_tbl("ItemTbl")
# matchStatsTbl <- read_tbl("MatchStatsTbl")
# matchTbl <- read_tbl("MatchTbl")
# RankTbl <- read_tbl("RankTbl")
# SummonerMatchTbl <- read_tbl("SummonerMatchTbl")
# TeamMatchTbl <- read_tbl("TeamMatchTbl")

```


## Modified Tables
## Champion Table -VA

The following the data set has basically an NA value named 'No champion'. The data set has been updated so that it only represents actual champions that are playable in League of Legends.

```{r}
championTbl %>%
  slice_head(n = 20) %>%           
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```


## MSI Table -TY
Creating a new table called 'MSI_Tbl' to join the Match Stats table and Item Table




What we did is join most of our data sets to have a more efficient data structure. The following data sets were created:
 - match_rank_tbl : This table displays every match in EU region with the following information: Queue type, Rank, Game duration. 
 - MSI_Tbl : This data set will display the players detailed match stats which include kills for both enemy champions and monsters affiliated and include item purchase and summoner spells.
 - SMR_Tbl : This data set displays the players detailed 


```{r, echo=FALSE}
match_rank_tbl %>%
  slice_head(n = 20) %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```


## TMR Tbl -TY
Create new table called 'TMM_Tbl' to join Team Match Table and Match Table

```{r, echo = F}
TMR_Tble %>%
  slice_head(n = 20) %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```


## SMR tbl -VA

The following table was created in order to join both the summoner match table and a match rank table.
This table displays a smaller depiction 


```{r, echo=FALSE}
SMR_Tbl %>%
  slice_head(n = 20) %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```


## Tamana MSI_tbl and Match_rank_tbl dplyr and plot functions

#MSI_Tbl

MSI_Tbl
```{r, echo=FALSE}
 MSI_Tbl %>%
  slice_head(n = 20) %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

1. How many SummonerMatchFk play more than one lane


```{r, echo=FALSE}
MSI_Tbl %>%
  group_by(SummonerMatchFk)%>%
  summarise(num_lanes = n_distinct(Lane))%>% #count the unique lanes
  filter(num_lanes > 1)%>%
  summarise(total_players = n())

```


2.Find the Mean, Median, Max, and Min for the following:
- minions killed
- TurretDmg
- DmgTaken
- DmgDealt
- totalGold.


mean, median, min, and max of DmgDealt:
```{r, echo = F}

MSI_Tbl%>%
  ungroup() %>% 
  summarise('Avg Gold Total'= mean(TotalGold, na.rm = T),
            'Median Total Gold' = median(TotalGold, na.rm = T), 
            'Min Total Gold' = min(TotalGold, na.rm = T),
            'Max Total Gold' = max(TotalGold, na.rm = T),
            'Avg Minions Killed' = mean(MinionsKilled, na.rm = T),
            'Median Minions Killed' = median(MinionsKilled, na.rm = T),
            'Min Minions Killed' = min(MinionsKilled, na.rm = T),
            'Max Minions Killed' = max(MinionsKilled, na.rm = T),
            'Avg Damage Dealt' = mean(DmgDealt, na.rm = T),
            'Median Damage Dealt' = median(DmgDealt, na.rm = T), 
            'Min Damage Dealt' = min(DmgDealt, na.rm = T),
            'Max Damage Dealt' = max(DmgDealt, na.rm = T),
            'Avg Damage Taken' = mean(DmgTaken, na.rm = T),
            'Median Damage Taken' = median(DmgTaken, na.rm = T), 
            'Min Damage Taken' = min(DmgTaken, na.rm = T),
            'Max Damage Taken' = max(DmgTaken, na.rm = T),
            'Avg Turret Damage Dealt' = mean(TurretDmgDealt, na.rm = T),
            'Median Turret Damage Dealt' = median(TurretDmgDealt, na.rm = T),
            'Min Turret Damage Dealt' = min(TurretDmgDealt, na.rm = T), 
            'Max Turret Damage Dealt' = max(TurretDmgDealt, na.rm = T)) %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "170px")

```





3. Create new column (boolean) for indicating win or lose. Filter to win and lose only and create a ggplots.

```{r, echo = F}
MSI_Tbl%>%
  mutate(won = Win != 1)%>%
  drop_na(won)%>% 
  ggplot(aes(x=won, fill=won)) + 
  geom_bar() +
  labs(title = "Win vs. Lose")
```

# Created a new column called SecondLane 
```{r, echo=FALSE}
MSI_Tbl %>% 
   group_by(SummonerMatchFk) %>% 
  filter(n()>1) %>%   
  distinct(SummonerMatchFk, Lane, .keep_all = TRUE) %>% 
  arrange(SummonerMatchFk) %>%   
  filter(n()>1) %>% 
  group_by(SummonerMatchFk) %>% 
  mutate(tally_person = row_number()) %>% 
  filter(tally_person == 2) -> table2

MSI_Tbl %>% 
   group_by(SummonerMatchFk) %>% 
  filter(n()>1) %>%   
  distinct(SummonerMatchFk, Lane, .keep_all = TRUE) %>% 
  arrange(SummonerMatchFk) %>%   
  filter(n()>1) %>% 
  group_by(SummonerMatchFk) %>% 
  mutate(tally_person = row_number()) %>% 
  filter(tally_person == 1) %>%  
  select(SummonerMatchFk, SecondLane = Lane) -> table1

MSI_Tbl_doubles <- full_join(table1, table2, join_by(SummonerMatchFk))
rm(table1)
rm(table2)


MSI_Tbl <- MSI_Tbl %>% 
  group_by(SummonerMatchFk) %>% 
  anti_join(MSI_Tbl_doubles, join_by(SummonerMatchFk)) %>%
  mutate(SecondLane = NA) %>% 
  rbind(MSI_Tbl_doubles) %>% 
  distinct(SummonerMatchFk, .keep_all = TRUE) %>%
  select(-tally_person, -item1, -item2,-item3, -item4, -item5,-item6) %>% 
  arrange(SummonerMatchFk) 

rm(MSI_Tbl_doubles)

```

4. MSI_tbl (ask professor) Items, filter NAs from item names, count total items, most popular items, least popular items. Median and mean items a player holds. 

```{r, echo=FALSE}
#Removing NAs from the MSI_Tbl
temp_MSI <- MSI_Tbl%>%
  drop_na(ItemName, ItemName_2, ItemName_3, ItemName_4, ItemName_5, ItemName_6)

#Combining the item name columns into one single column
temp_MSI_Tbl <- MSI_Tbl%>%
  pivot_longer(
    cols = starts_with("ItemName"), # automatically combines columns
    names_to = "Items",             # new column that stores old columns 
    values_to = "ItemNames"         # new column that has the combined columns
     )

#Count the total number of items
new_temp_MSI_Tbl <- temp_MSI_Tbl %>% 
  group_by(ItemNames) %>% 
  summarise(Total_Items=n())

#Find most popular items
new_temp_MSI_Tbl%>% 
  slice_max(Total_Items, n=10)

#least popular item
new_temp_MSI_Tbl %>% 
  slice_min(Total_Items)

#join temp_MSI_Tbl and new_temp_MSI_Tbl to get the mean and median of items a player holds.
N_MSI_Tbl <- full_join(temp_MSI_Tbl, new_temp_MSI_Tbl, by = join_by(ItemNames)) 


#Mean and median of items a player holds
new_temp_MSI_Tbl %>% 
  drop_na(ItemNames) %>% 
  group_by(ItemNames) %>% 
  summarise(Items_used_avg = mean(Total_Items), 
            Items_used_median = median(Total_Items))


```


5. Plot game duration as the Y value and Queue type as the X value, filter based on RankName.
```{r, echo=FALSE}
match_rank_tbl %>%
  group_by(RankName)%>%
  summarise(Duration= n())

ggplot(match_rank_tbl, aes(x = GameDuration, color= QueueType)) + 
  geom_density() + 
  labs(title = "Game Duration")
```


```{r, echo=FALSE}
ggplot(matchStatsTbl, aes(x= kills, color = Lane)) + geom_density() + facet_wrap(~Lane)
```



6. Analyze if totalgold or dmgdealt increases the chances of winning
```{r, echo=FALSE}
ggplot(MSI_Tbl, aes(x = TotalGold, y = DmgDealt, color = Win)) + geom_point(alpha = 0.3) + 
  labs(title="Win: Total Gold vs Damage Dealt",
       x = "Total Gold",
       y = "Damage Dealt")
  
```

7. Plot top 10 popular items 
```{r,echo=FALSE}
Top_Items <- new_temp_MSI_Tbl%>% 
  slice_max(Total_Items, n = 10)

ggplotly(ggplot(Top_Items %>% 
                  drop_na(ItemNames), aes(x=ItemNames, y = Total_Items, fill = ItemNames, text = paste("Count:", after_stat(y)))) + geom_col() + 
           labs(
             title ="Top 10 Items",
             x = "Item Names",
             y = "Total Items"), tooltip = "text")

``` 


```{r, echo=FALSE}
#Remove temporary MSI tables not needed
rm(temp_MSI)
rm(Top_Items)
rm(new_temp_MSI_Tbl)
rm(N_MSI_Tbl)
rm(temp_MSI_Tbl)
```


8. Plot top 10 champions
```{r,echo=FALSE}
champs <- SMR_Tbl %>%
  group_by(ChampionName) %>% 
  summarise(num_champs = n())
```

```{r, echo=FALSE}

Top_champs <- champs %>% 
  slice_max(num_champs, n = 10)

ggplotly(ggplot(Top_champs, aes(x = ChampionName, y = num_champs, fill = ChampionName, text = paste("Count:", after_stat(y)))) + geom_col() + 
           labs(title = "Top 10 Champions", 
                x = "Champions Name",
                y = "Number of Champions"), tooltip = "text")
```

```{r, echo=FALSE}
#Remove extra tables not needed 
rm(Top_champs)
rm(champs)
```

#Second Lane Data analysis for MSI Kills Column plot
```{r, echo=FALSE}
ggplotly(ggplot( MSI_Tbl %>% 
  select(SecondLane,kills,SummonerMatchFk) %>% 
  drop_na(SecondLane) %>% 
  group_by(SecondLane) %>%
  count(SecondLane, wt = kills) %>% 
  rename(kills = n), 
  aes(x = SecondLane, y = kills, fill = SecondLane, text = paste("Count:", after_stat(y))))
  + geom_col(), 
  tooltip = "text", 
  na.rm = TRUE )

```
  

#Lane Data analysis for MSI Kills Column plot
```{r, echo=FALSE}
ggplotly(ggplot( MSI_Tbl %>% 
  select(Lane,kills,SummonerMatchFk) %>% 
  drop_na(Lane) %>% 
  group_by(Lane) %>%
  count(Lane, wt = kills) %>% 
  rename(kills = n), 
  aes(x = Lane, y = kills, fill = Lane, text = paste("Count:", after_stat(y))))
  + geom_col() + labs(title= "Kills vs Lane"), 
  tooltip = "text", 
  na.rm = TRUE )

```


10. Find mean, min, max of visionscore and plot mean of visionScore for winning and loosing teams


```{r,echo=FALSE}
VS <-MSI_Tbl %>% 
  mutate(Win = ifelse(Win==0, "Lose", "Win")) %>% 
  group_by(Win) %>% 
  summarise(VS_avg = mean(visionScore, na.rm =T),
            VS_min = min(visionScore, na.rm =T), 
            VS_max = max(visionScore, na.rm =T)) %>%
  drop_na(Win)

```

```{r, echo=FALSE}
ggplot(VS, aes(x = Win, y = VS_avg, fill = Win)) +
  geom_col() + 
  labs(
   title = "Vision Score: Winning vs Losing",
       x = "win/lose",
       y = "Vision Score Average"
    )

```

```{r, echo=FALSE}
#Remove temp table VS
rm(VS)
```

11. Analyze if higher visionScore mean more wins
```{r, echo=FALSE}
ggplot(MSI_Tbl %>% 
         mutate(Win = ifelse(Win == 0, "Lose","Win")), aes(x = visionScore, color = Win)) + geom_density(alpha = 0.4) + 
  labs(title = "Vision Score: Winning vs Losing Teams",
       x= "Vision Score")
```


```{r}

```


```{r}

```


```{r}

```


## Veronica

1. TMR_tbl create column (boolean) indicating who won. Lets combine TMR with Champion Table 

```{r, echo=FALSE}
ggplot(TMR_Tble %>% 
         mutate(BlueWin = ifelse(BlueWin == 0,"Lose","Win")) %>% 
         drop_na(QueueType) %>% 
         drop_na(BlueWin), aes(x= GameDuration, y = BlueKills, color = BlueWin )) + geom_jitter(alpha = 0.4) + facet_wrap(~QueueType)

```


```{r, echo=FALSE}
ggplot(TMR_Tble %>% 
         mutate(RedWin = ifelse(RedWin == 0,"Lose","Win")) %>% 
         drop_na(QueueType) %>% 
         drop_na(RedWin), aes(x= GameDuration, y = RedKills, color = RedWin )) + geom_jitter(alpha = 0.4) + facet_wrap(~QueueType)

```

```{r}
TMR_Tble %>% 
  mutate(TotalKills = rowSums(across(c(RedKills, BlueKills)), na.rm = TRUE)) %>% 
  count(Winning_Team, wt = TotalKills) 

```

```{r, echo=FALSE}
ggplot(TMR_Tble %>% 
         mutate(TotalKills = rowSums(across(c(RedKills, BlueKills)), na.rm = TRUE)), aes(x = GameDuration, y = TotalKills)) + geom_jitter(alpha = 0.2)

```


```{r}
Team_Winner_Tbl %>% 
  count(Side, wt = Kills)
```

```{r, echo=FALSE}
ggplot(Team_Winner_Tbl, aes(x = GameDuration, y = Kills, color = Side)) + geom_jitter( alpha= 0.5)

```

```{r, echo=FALSE}
ggplotly(ggplot(Team_Winner_Tbl, aes(x = GameDuration, y = Kills, color = QueueType)) + geom_point(alpha = 0.2))

```



```{r}

```




```{r}

```




```{r}

```





2. TMR_tbl Filter teams with winning arams, classics based on rank. Bar graph & scatter plot x = rank, y = # of wins, color by queue types, density. face wrap

Let us look at all winning teams from each map type.
```{r, echo=FALSE}
#source(here::here("WinningTeams","app.R"))
#shinyApp(ui, server) 
#head(Team_Winner_Tbl, n = 10) 
```


3. TMR_tbl Filter winning teams, most used champion in red team and blue team 

```{r, echo=FALSE}
ggplot(Team_Winner_Tbl, aes(x = GameDuration, color = Side)) + geom_density() 

```

```{r,echo=FALSE}

ggplot(Team_Winner_Tbl, aes(x = GameDuration, color = RankName)) + geom_density() + facet_wrap(~RankName)

```


```{r, echo=FALSE}
common_theme <- theme_minimal(base_size = 14) +
  theme(
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 10)
  )

```


```{r, echo=FALSE}
#Team win statistics : mean, min, max forKills, Baron, Rift Herald, Dragon, Towers

Team_Winner_Stats <-Team_Winner_Tbl %>%
  filter(Side %in% c("Red","Blue")) %>%
  filter(QueueType %in% c("CLASSIC", "ARAM","SWIFTPLAY","ULTBOOK")) %>% 
  group_by(Side, QueueType) %>% 
  summarise(MeanKills = mean(Kills, na.rm = TRUE),
            MinKills = min(Kills, na.rm = TRUE),
            MaxKills = max(Kills, na.rm = TRUE),
            MeanBaron = mean(BaronKills, na.rm = TRUE),
            MinBaron = min(BaronKills, na.rm = TRUE),
            MaxBaron = max(BaronKills, na.rm = TRUE),
            MeanRiftHeraldKills = mean(RiftHeraldKills, na.rm = TRUE),
            MinRiftHeraldKills = min(RiftHeraldKills, na.rm = TRUE),
            MaxRiftHeraldKills = max(RiftHeraldKills, na.rm = TRUE),
            MeanDragonKills = mean(DragonKills, na.rm = TRUE),
            MinDragonKills = min(DragonKills, na.rm = TRUE),
            MaxDragonKills = max(DragonKills, na.rm = TRUE),
            MeanTowerKills = mean(TowerKills, na.rm = TRUE),
            MinTowerKills = min(TowerKills, na.rm = TRUE),
            MaxTowerKills = max(TowerKills, na.rm = TRUE)) 


Team_Winner_Stats %>% 
  rename('Queue Type' = QueueType) %>% 
  rename('Mean Kills' = MeanKills) %>% 
  rename('Min Kills' = MinKills) %>% 
  rename('Max Kills'= MaxKills) %>% 
  rename('Mean Baron' = MeanBaron) %>% 
  rename('Min Baron' = MinBaron) %>% 
  rename('Max Baron' = MaxBaron) %>% 
  rename('Mean Rift Herald Kills' = MeanRiftHeraldKills) %>% 
  rename('Min Rift Herald Kills' = MinRiftHeraldKills) %>% 
  rename('Max Rift Herald Kills' = MaxRiftHeraldKills) %>% 
  rename('Mean Dragon Kills' = MeanDragonKills) %>% 
  rename('Min Dragon Kills' = MinDragonKills) %>% 
  rename('Max Dragon Kills' = MaxDragonKills) %>% 
  rename('Mean Tower Kills' = MeanTowerKills) %>% 
  rename('Min Tower Kills' =MinTowerKills) %>% 
  rename('Max Tower Kills' =MaxTowerKills) %>% 
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "175%", height = "400px")


```

```{r, echo=FALSE}
# Bar plot 
# ```{r}
# ggplotly(ggplot(Team_Winner_Stats, aes(x = QueueType, y = MeanKills, fill = Side,text = paste("Count:", after_stat(y)))) + geom_col() + facet_wrap(~Side), tooltip = "text")
# ```
# 
# ```{r}
# ggplotly(ggplot(Team_Winner_Stats %>% 
#                   filter(QueueType!= "ARAM"), aes(x = QueueType, y = MeanBaron, fill = Side,text = paste("Count:", after_stat(y)))) + geom_col() + facet_wrap(~Side), tooltip = "text")
# ```
# 
# ```{r}
# ggplotly(ggplot(Team_Winner_Stats %>% 
#                   filter(QueueType!= "ARAM"), aes(x = QueueType, y = MeanRiftHeraldKills, fill = Side,text = paste("Count:", after_stat(y)))) + geom_col() + facet_wrap(~Side), tooltip = "text")
```

# Mean of Kills, Baron Kills, Rift Herald Kills, Dragon Kills, Tower Kills 

```{r, echo=FALSE}
a1 <- ggplot(Team_Winner_Stats, aes(x = QueueType, y = MeanKills, fill = Side)) + geom_col(width = 1) + ggtitle("Average Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")

a2 <- ggplot(Team_Winner_Stats %>% 
               filter(QueueType != "ARAM"), aes(x = QueueType, y = MeanBaron, fill = Side)) + geom_col(width = 1) + ggtitle("Average Baron Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")

a3 <- ggplot(Team_Winner_Stats %>% 
               filter(QueueType != "ARAM") %>% 
               filter(MeanRiftHeraldKills != 0), aes(x = QueueType, y = MeanRiftHeraldKills, fill = Side)) + geom_col(width = 1) + ggtitle("Average Rift Herald Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")

a4 <- ggplot(Team_Winner_Stats %>% 
               filter(QueueType != "ARAM"), aes(x = QueueType, y = MeanDragonKills, fill = Side)) + geom_col(width = 1) + ggtitle("Average Dragon Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")
 
a5 <- ggplot(Team_Winner_Stats, aes(x = QueueType, y = MeanTowerKills, fill = Side)) + geom_col(width = 1) + ggtitle("Average Tower Kills") + coord_flip() + common_theme + labs(y = NULL, x = NULL) 

```


```{r, echo= FALSE}
grid.arrange(a1,a3,a4,a5,a2, nrow = 3, ncol = 2, top = "Team Winner Statistics", left = "Queue Type", bottom = "Average Count")

```

#Max of Kills, Baron Kills, Rift Herald Kills, Dragon Kills, Tower Kills 

```{r}
b1 <- ggplot(Team_Winner_Stats, aes(x = QueueType, y = MaxKills, fill = Side)) + geom_col(width = 1) + ggtitle("Max Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL)  + guides(fill = "none")

b2 <- ggplot(Team_Winner_Stats %>% 
               filter(QueueType != "ARAM"), aes(x = QueueType, y = MaxBaron, fill = Side)) + geom_col(width = 1) + ggtitle("Max Baron Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")

b3 <- ggplot(Team_Winner_Stats %>% 
               filter(QueueType != "ARAM") %>% 
               filter(MeanRiftHeraldKills != 0), aes(x = QueueType, y = MaxRiftHeraldKills, fill = Side)) + geom_col(width = 1) + ggtitle("Max Rift Herald Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")

b4 <- ggplot(Team_Winner_Stats %>% 
               filter(QueueType != "ARAM"), aes(x = QueueType, y = MaxDragonKills, fill = Side)) + geom_col(width = 1) + ggtitle("Max Dragon Kills") + coord_flip() + common_theme + labs(x = NULL, y = NULL) + guides(fill = "none")
 
b5 <- ggplot(Team_Winner_Stats, aes(x = QueueType, y = MaxTowerKills, fill = Side)) + geom_col(width = 1) + ggtitle("Max Tower Kills") + coord_flip() + common_theme + labs(y = NULL, x = NULL) 

```


```{r}
grid.arrange(b1,b3,b4,b5,b2, nrow = 3, ncol = 2, top = "Team Winner Statistics", left = "Queue Type", bottom = "Max Count")

```

7.each player and the amount of games they play per queue type 

```{r, echo=FALSE}
Player_Games <- SMR_Tbl %>% 
  select(SummonerFk,QueueType,RankFk,RankName) %>% 
  group_by(QueueType, SummonerFk, RankName) %>%
  summarise(games = n()) %>% 
  arrange(SummonerFk)

```

How many players play in each queue type, a player can play multiple queue types in league of legends. No map restriction.
```{r}

ggplotly(ggplot(Player_Games %>% 
                  drop_na(QueueType),aes(x = QueueType, fill = QueueType, text = paste("Count:", after_stat(count)))) + geom_bar(), tooltip = "text", na.rm = TRUE)

```

```{r}
Player_Games %>%
  group_by(RankName) %>% 
  distinct(SummonerFk,.keep_all = TRUE) %>% 
  summarise(n=n()) %>% 
  drop_na(RankName) %>% 
  rename(Players = n)
```

What rank players fall in in this data set. 

```{r}
ggplotly(ggplot(Player_Games %>%
  group_by(RankName) %>% 
  distinct(SummonerFk,.keep_all = TRUE) %>% 
  summarise(n=n()) %>% 
  drop_na(RankName) %>% 
  rename(Players = n),aes(x = RankName, y = Players, fill = RankName, text = paste("Count:", after_stat(y)))) + geom_col(), tooltip = "text", na.rm = TRUE)

```

Fun fact: 
```{r}
#letsgo 
```

