---
title: "LOL_Dataset_Project"
author: "Tamana Yaqoubi, Veronica Alviso"
date: "2025-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(gridExtra)

```

## Read csv files
```{r}
championTbl <- read.csv("ChampionTbl.csv")
itemTbl<- read.csv("ItemTbl.csv")
matchStatsTbl <- read.csv("MatchStatsTbl.csv")
matchTbl <- read.csv("MatchTbl.csv")
RankTbl <- read.csv("RankTbl.csv")
SummonerMatchTbl <- read.csv("SummonerMatchTbl.csv")
TeamMatchTbl <- read.csv("TeamMatchTbl.csv")
```

## View datasets
```{r}
head(championTbl) %>% knitr::kable()
head(itemTbl) %>% knitr::kable()
head(matchStatsTbl) %>% knitr::kable()
head(matchTbl) %>% knitr::kable()
head(RankTbl) %>% knitr::kable()
head(SummonerMatchTbl) %>% knitr::kable()
head(TeamMatchTbl) %>% knitr::kable()
```

## Including Plots

Create a new table that combines 



```{r}
itemTbl %>% 
  filter(ItemID == "2055")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


## Champion Table -VA





```{r}

```





## MSI Table -TY
Creating a new table called 'MSI_Tbl' to join the Match Stats table and Item Table




```{r}
MSI_Tbl <- full_join(matchStatsTbl, itemTbl, 
                     by = join_by(item1 == ItemID),
                     suffix = c("", "_1"))

MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item2 == ItemID), 
                     suffix = c("", "_2"))

MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item3 == ItemID), 
                     suffix = c("", "_3"))

MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item4 == ItemID), 
                     suffix = c("", "_4"))


MSI_Tbl  <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item5 == ItemID), 
                     suffix = c("", "_5"))


MSI_Tbl <- full_join(MSI_Tbl, itemTbl, 
                     by = join_by(item6 == ItemID), 
                     suffix = c("", "_6"))

MSI_Tbl

```





## match_rank Table -VA





```{r}

```





## TMM Tbl -TY
Create new table called 'TMM_Tbl' to join Team Match Table and Match Table



```{r}
TMM_Tbl <- full_join(TeamMatchTbl, matchTbl, by = join_by(MatchFk == MatchId))
TMM_Tbl

TMR_Tble <- full_join(TeamMatchTbl, match_rank_tbl, by = join_by(MatchFk == MatchId))
```





## SMR tbl -VA





```{r}

```





